### 2012-02-07 GUIErrorDetector/paper/introduction.tex
small revise

Our static analysis is independent of the call graph construction algorithm.
Given a sound call graph, our analysis is sound in that it does
not miss true positives. GUI applications tend to use reflection, and
in the presence of reflection, existing call graph construction algorithms such as RTA~\cite{rta}
and k-CFA~\cite{kcfa} fail to build a good call graph.
To alleviate this problem, we present an algorithm to build reflection-aware call graph, and
also compare its usefulness with existing call graph construction algorithms in
our experiments. Static analysis may report false positives due to its
conservative nature, or multiple warnings that actually correspond
to the same error. To address such limitations, we devise a set
 of heuristics to filter likely false positives and redundant warnings.

@@

Our tool works in a fully automatic, push-button manner,
and scales to realistic programs.
We evaluated our implementation on 9 programs comprising over 76000 LOC.
The experiment results demonstrate
that: our technique is effective (it found 11 real-world errors
from four supported frameworks and produced only 10 false positive warnings);
our reflection-aware call graph construction algorithm helps in
finding errors in Android applications;
and our proposed heuristics significantly reduce the number of
false positives and redundant warnings.

@@

\item \textbf{Evaluation.} We applied our tool to 9 programs 
from 4 different frameworks, comprising over 76000 LOC. The results
show the usefulness of the proposed technique (Section~\ref{sec:evaluation}).

>>>>

Our static analysis is independent of the call graph construction algorithm.
Given a sound call graph, our analysis is sound in that it does
not miss true positives. GUI applications tend to use reflection, and
in the presence of reflection, existing call graph construction algorithms such as RTA~\cite{rta}
and k-CFA~\cite{kcfa} fail to build a good call graph.
To alleviate this problem, we present an algorithm to build reflection-aware call graph, and
also compare its usefulness with existing call graph construction algorithms in
our experiments. Static analysis may report false positives due to its
conservative nature, or multiple warnings that actually correspond
to the same error. To address such limitations, we devise a set
 of error filters to remove likely false positives and redundant warnings.

@@

Our tool works in a fully automatic, push-button manner,
and scales to realistic programs.
We evaluated our implementation on \subnum programs comprising \totaloc LOC.
The experiment results demonstrate
that: our technique is effective (it found \bugs real-world errors
from four supported frameworks and produced only \falses false positive warnings);
our reflection-aware call graph construction algorithm helps in
finding errors in Android applications;
and our proposed filters significantly reduce the number of
false positives and redundant warnings.

@@

\smallstep

\item \textbf{Evaluation.} We applied our tool to \subnum programs 
from 4 different frameworks, comprising \totaloc LOC. The results
show the usefulness of the proposed technique (Section~\ref{sec:evaluation}).

### 2012-02-07 GUIErrorDetector/paper/technique.tex
small revise

We first give a high-level formulation of the problem, then present
the error detection algorithm. Finally, we show how to instantiate
the error algorithm for different GUI frameworks.

@@

Our algorithm in Figure~\ref{fig:detectalgorithm} %works as follows. It
first constructs a static call graph for the tested program (line 2),
then specifies entry nodes, UI-accessing nodes, and safe UI nodes
for it on line 3, 4, and 5, respectively. Lines 3--5 are GUI framework-specific.
As an example, for a SWT desktop application, the entry nodes include
the single main method, UI-accessing nodes include methods
\CodeIn{Display.checkWidget} and \CodeIn{Display.checkDevice},
and safe UI methods include two SWT helper methods \CodeIn{Display.asyncExec}  and
\CodeIn{Display.syncExec} for message passing. The detailed instantiation
for each supported framework is explained in Section~\ref{sec:platforms}.

The algorithm first performs graph traversal to find all reachable \CodeIn{Thread.start()}
nodes from the entry nodes (line 6).
%For each entry node, the algorithm uses standard Breadth First Search (BFS)
%to find all reachable \CodeIn{Thread.start()} nodes (line 7).
Each \CodeIn{Thread.start()} node in a call graph indicates that a new,
non-UI thread is spawned.  The \CodeIn{Thread.start()}
nodes act as the sources in the main graph traversal.
The algorithm uses BFS to search for reachable UI-accessing
methods (lines 10 -- 24).
The algorithm stops the traversal if it reaches a UI-accessing
method (lines 16 -- 18) or a safe UI method (lines 19, 20).
%Specifically, it uses a queue to keep track of the nodes to be visited (line 7),
%and stores all visited nodes to avoid infinite loop (line 8).
%The algorithm checks every successive node to be visited (line 16):
%it reports an error if that node is a UI-accessing method (lines 18, 19), or skips
%it if it is a safe UI method (lines 20, 21), or simply keeps traversing otherwise (line 23).

The error message created by the method \CodeIn{createErrorReport} on line 17
includes the method call chain from the entry node to the UI-accessing node
as the error report. For brevity, we do not show the data structures that store
the current call chain.
Figure~\ref{fig:report} shows a method call chain from the entry
node \CodeIn{LayerView.<init>} to the UI-accessing node \CodeIn{ViewRoot}.\CodeIn{checkThread}.
%Note that when the algorithm determines that a UI-accessing method may be invoked
%by a non-UI thread, it computes a method call chain from the entry node to
%the UI-accessing node as the error report.
% does that.

\begin{figure}[t]
\textbf{Input}: a Java program $\mathit{P}$\\
\textbf{Output}: a set of potential invalid thread access errors\\
%\textbf{Auxiliary Methods:}\\
%getSuccNodes($\mathit{g}$, $\mathit{n}$): return node $\mathit{n}$'s successive
%nodes in the graph $\mathit{g}$\\
\vspace{-4mm}
\begin{algorithmic}[1]
\STATE $\mathit{errors}$ $\leftarrow$ $\emptyset$ 
\STATE $\mathit{cg}$ $\leftarrow$ constructCallGraph($\mathit{P}$)
\STATE $\mathit{entryNodes}$ $\leftarrow$ getEntryNodes($\mathit{cg}$)
\STATE $\mathit{uiAccessingNodes}$ $\leftarrow$ getUIAccessNodes($\mathit{cg}$)
\STATE $\mathit{safeUINodes}$ $\leftarrow$ getSafeNodes($\mathit{cg}$)\\
\COMMENT{get all reachable \CodeIn{thread.start()} nodes from entry nodes}
\STATE $\mathit{threadStarts}$ $\leftarrow$ $\bigcup_{entry \in entryNodes}$ getReachableStarts($\mathit{entry}$)
\COMMENT{keep the nodes to be visited next in a worklist}
\STATE $\mathit{worklist}$ $\leftarrow$ an empty queue\\
\STATE $\mathit{worklist}$.enqueueAll($\mathit{threadStarts}$)
\STATE $\mathit{visited}$ $\leftarrow$ $\emptyset$
\WHILE{$\mathit{worklist}$.isNotEmpty()}
\STATE $\mathit{node}$ $\leftarrow$ $\mathit{worklist}$.dequeue()
\IF{$\mathit{node}$ $\in$ $\mathit{visited}$}
\STATE continue
\ENDIF
\STATE $\mathit{visited}$ $\leftarrow$ $\mathit{visited}$ $\cup$ $\mathit{node}$
\IF{$\mathit{node}$ $\in$ $\mathit{uiAccessingNodes}$}
\STATE $\mathit{newError}$ $\leftarrow$ createErrorReport($\mathit{node}$)
\STATE $\mathit{errors}$ $\leftarrow$ $\mathit{errors}$ $\cup$ $\mathit{newError}$
\ELSIF{$\mathit{node}$ $\in$ $\mathit{safeUINodes}$}
\STATE continue
\ELSE
\STATE $\mathit{worklist}$.enqueueAll(getSuccNodes($\mathit{cg}$, $\mathit{node}$))
\ENDIF 
\ENDWHILE
\RETURN $errors$
%\ENDWHILE
\vspace{-2mm}
\end{algorithmic}
\caption{Algorithm for detecting invalid thread access errors in multithreaded GUI programs. 
Any call graph construction algorithm can be used (line 2). The algorithm
is parameterized by the three methods in lines 3--5 which are specific to each GUI framework
 as described in Section~\ref{sec:platforms}.
} \label{fig:detectalgorithm}
\end{figure}

@@

Given a sound call graph, our algorithm is sound in that it does not
miss true positives. We note, however, that computing a sound
call graph in the presence of reflection is non-trivial. 
To alleviate this problem, we next proposed a reflection-aware call graph
construction algorithm in Section~\ref{sec:cg}.

\subsubsection{Reflection-aware Call Graph Construction}
\label{sec:cg}

@@

When analyzing the code in Figure~\ref{fig:sampleandroid}, existing call graph algorithms
fail to conclude that the variable \CodeIn{button} declared at line 6
points to a \textit{non-null} \CodeIn{Button} object due to its limitation in deal with the
reflection call \CodeIn{findViewById}. As a result, the built 
call graph will exclude the calling edge corresponding to the
\CodeIn{setText} method call on line 10.

@@

As demonstrated in our experiments, using this reflection-aware call
graph construction algorithm helps in detecting errors
in Android applications (Section~\ref{sec:evaluation}).

@@

Our static analysis takes the call relationship specified by this
annotation into consideration when traversing the call graph. 
Adding annotations for native methods is optional and requires manual effort.
In our experiments, 1 out of 9 programs uses native methods. We manually
searched the source files, inspected the code to determine possible target methods
that may be called by a native method, and added 7 annotations for this program.
We found such an annotation was useful: one error
can only be reported with using the user-provided annotations.

\subsubsection{Heuristic Filtering}
\label{sec:heuristic}

A static analysis can exhaustively check possible error paths; but may report
paths that do not actually exist (false positives) or multiple paths
 that have the same error cause (redundant warnings). We devise
5 heuristic filters below to remove likely false positives and redundant warnings.
The first two are for eliminating false positives, while the
other three are for reducing redundant warnings.

@@

%\item
\textbf{1. Filter Reports Containing Library Calls}. A
method call chain containing certain library calls
like \CodeIn{Runtime.}\CodeIn{shutDown} are unlikely to
be buggy. For example, the \CodeIn{Runtime.}\CodeIn{shutDown}
method is called when JVM terminates, and uses multithreading
to dispose all GUI objects when the program exits.
We encoded a list of common library calls by proposing
a basic set of library calls that seemed natural and
generally applicable, based on our programming experience.
We later added other calls we found helpful in analyzing
programs and that we believed would be generally useful.
%We encode a list of common library calls, and remove
%a reported warning if it contains one of them.
%Method call chain involves typical
%system methods like \CodeIn{toString} are unlikely to reveal a real bug.

%\item
\textbf{2. Filter Reports With User-Annotated Methods}. Besides general
library calls, users are also permitted to explicitly annotate methods
that will never trigger an error.
For example, the Android GUI framework provides a utility method 
\CodeIn{runOnUIThread} to check whether the current thread is the UI thread
before executing the code. If the current thread is not the UI thread,
this method will be executed on the UI thread via message passing.
Thus, a reported method call chain containing an annotated 
can be safely removed. We produced the list of annotated methods
during analyzing programs on different GUI frameworks; we did this
only between experiments rather than biasing experiments by tuning
our tool to specific programs.

%\item
\textbf{3. Filter Lexically Redundant Reports}. One reported method call
chain can lexically subsume another one. For example, suppose that two
reported method call chains: \CodeIn{a()} $\rightarrow$ \CodeIn{b()}
$\rightarrow$ \CodeIn{c()} and 
\CodeIn{d()} $\rightarrow$ \CodeIn{a()} $\rightarrow$ \CodeIn{b()} $\rightarrow$ \CodeIn{c()}
both lead to a potential error, since $\CodeIn{d()}$ and \CodeIn{a()}
are two distinct entry methods. The second call chain should
be removed and would not reduce the error detection capability, since
the first chain reveals the same error and is shorter 
for programmers to interpret.

%\item
\textbf{4. Filter Report With the Same Head Methods from the Entry Node to \CodeIn{Thread.start()}}. A method can call
multiple methods that access GUI objects, such as:
\vspace{-1mm}
\begin{CodeOut}
\begin{alltt}
     public void m() \{
         accessUIObject1();
         accessUIObject2();
     \}
\end{alltt}
\end{CodeOut}
If method \CodeIn{m()} is invoked by a non-UI thread, method call chains
only different at the last few method nodes may be reported separately, such as:

@@

Among the above 5 filters, filters 2 and 3 are sound
in that they will not filter real bugs, and other 3 filters
are based on heuristics. However, as we will show in
our experiments, these filters work remarkably well in practice (Section~\ref{sec:filters}).

\subsection{Instantiation for Different Frameworks}
\label{sec:platforms}

We instantiated our error detection technique for four popular GUI frameworks:
SWT, Eclipse plugin, Swing, and Android.
The major framework-specific parts, corresponding to
lines 3 -- 5 in Figure~\ref{fig:detectalgorithm}, are identifying
\textbf{call graph entry nodes}, \textbf{UI-accessing nodes},
and \textbf{safe UI methods} for each framework.

%For each framework, we customize the \textit{call graph entry nodes},
%\textit{UI-accessing nodes}, and \textit{safe UI methods} on lines 3 -- 5 of the
%algorithm in

%For the sake of efficiency, they are all using the single thread model.

%Why these platforms? popularity? account for xxx\% of the GUI.

%customizing for: entry points, starting points, error checking, thread
%safe UI methods, what is the event dispatching thread?

\subsubsection{SWT}

%SWT is an open source widget toolkit for Java designed to provide efficient,
%portable access to the GUI facilities of the operating systems
%on which it is implemented.
 We instantiated our technique for SWT applications as follows:

%starts from its main method.
%By default, the thread that the main method executes is the UI thread. Thus, we instantiate
%our technique as follows:

\begin{itemize}

\item \textbf{Call graph entry nodes: } the main method. Like a normal Java program,
a SWT desktop application has a single main method as the entry point. By default,
the main method is executed in the UI thread after the GUI
is initialized.

\item \textbf{UI-accessing nodes: } the \CodeIn{Display.checkWidget}
and \CodeIn{Display.} \CodeIn{checkDevice} methods. SWT uses the above
two methods to explicitly check thread accesses at runtime.
Any methods for manipulating GUIs object must call (one of) these two methods
 to determine whether the current thread is the UI thread or not.
%Thus, we treat nodes (in both user code and framework code) corresponding to the methods
%calling these two methods as UI-accessing nodes.
%must be invoked
%in the UI thread and as
%UI-accessing nodes.
 %methods to check whether the current thread is the UI thread or not. Thus,
%we treat all such methods that must be accessed in UI thread as the UI-accessing nodes.
% any
%methods that calls the checking method must be invoked in the UI thread.

\item \textbf{Safe UI methods: } SWT provides two helper methods (\CodeIn{Display.\\asyncExec}
and \CodeIn{Display.syncExec}) to execute code (a)synchro-
nizedly on the UI thread.
 We treat these two methods as safe UI methods, since invoking
them from any thread 
%are generally considered to be safe and
will not cause an invalid thread access error.

\end{itemize}

\subsubsection{Eclipse plugin}

We instantiated our technique for Eclipse plugin as follows:

%Unlike a SWT desktop application, an eclipse plugin, though is developed in SWT,
%has no single main method. Instead, (XXX) it extends certain extension points
%exposed by the eclipse framework, and eclipse will XXX. To instantiate our
%technique for the Eclipse plugin environment, we need to redefine the
%call graph entry points.

\begin{itemize}

\item \textbf{Call graph entry nodes: } all overridden SWT
GUI event handling methods in user code. An Eclipse plugin is built
on top of the SWT framework. However, unlike a SWT desktop application,
an Eclipse plugin does not have a main method as a single program entry point.
Instead, it extends extension points provided by the Eclispe framework to
implement functionalities. When a plugin starts, Eclipse
calls back the overridden methods to handle the
upcoming events. All SWT GUI event handling methods (i.e., the overriden
methods in the class that implements \CodeIn{org.eclipse.swt.internal.SWTEvent-\\Listener}) are
always called back from the UI thread, thus are used as call graph entry nodes.

\item \textbf{UI-accessing nodes} and \textbf{Safe UI methods} are the same as SWT.

\end{itemize}

\subsubsection{Swing}

A Swing application has a single main method, but contains three kinds of
threads: \textit{initial thread} that executes initial application code from the main method,
the \textit{UI thread}, where all GUI manipulation code is executed,
and the \textit{worker thread} where time-consuming background tasks are executed.
After a Swing program starts, its initial thread exits and the UI thread takes charge
of the application and starts to execute all event-handling code or spawns new worker threads. 
We instantiated our technique for Swing as follows:
%XXXX Therefore, we can not directly
%use the main method as the call graph entry point, since it is not invoked
%by the UI thread. We customize our technique for Swing as follows:

\begin{itemize}

\item \textbf{Call graph entry nodes:} all overridden Swing GUI event handling
methods in user code. Those event handling methods are always
called back from the UI thread, thus are used as call graph entry nodes.

\item \textbf{UI-accessing nodes:} %as stated in Swing's documentation,
all methods defined in each Swing GUI class except for three thread-safe
methods: \CodeIn{repaint()}, \CodeIn{revalidate()}, and \CodeIn{invalidate()}.

%methods in Swing GUI classes are not thread safe with three exceptions (\CodeIn{repaint()},
%\CodeIn{revalidate()}, and \CodeIn{invalidate()}). Thus, we
%treat nodes corresponding to those thread unsafe methods %in each GUI class
%as UI-accessing nodes.

\item \textbf{Safe UI methods: }  Swing's two helper methods
(\CodeIn{SwingUtilities.} \CodeIn{invokeLater} and \CodeIn{SwingUtilities.invokeAndWait}) that execute code on the UI thread.

\end{itemize}

\subsubsection{Android}

Android is a Java-based platform for embedded or mobile devices. 
An Android program does not have a single entry point but can
rather use parts of other Android applications on-demand and can require their
services by calling corresponding event handlers, directly or through the
operating system. In particular, Android applications use \textit{activities}
as code interacting with the user through a visual interface. GUI event handlers
are handled in an activity.
We instantiated our technique for Android programs as follows:
%, with some notable exceptions such as the
%lifecycle of activities.

%An XML \textit{manifest file} registers the components of an application. Other XML
%fies describe the visual layout of the activities. Activities \textit{inflate}
%layout files into
%visual objects (a hierarchy of views), through an \textit{inflater} provided by the An-
%droid library. This means that library or user-defined views are not explicitly
%created by new statements but rather inflated through \textit{reflection}. Library meth-
%ods such as \CodeIn{findViewById} access the inflated views.

\begin{itemize}

\item \textbf{Call graph entry nodes: }in an Android application,
an \CodeIn{Activity} object is created and manipulated by the UI thread. Thus, we treat
all public methods defined in the \CodeIn{Activity} class 
and any class in the user code that subclasses \CodeIn{Activity} as call graph entry nodes.
We also add all overridden Android GUI event handling methods in user
code as entry nodes, since they are also called back from the UI thread.

\item \textbf{UI-accessing nodes: }the \CodeIn{ViewRoot.checkThread} method.
Like SWT, Android explicitly checks whether
the current thread is a UI thread or not before accessing a GUI object via
the \CodeIn{ViewRoot.checkThread} method.
%method. This method is the only place where Android checks
%whether the current thread is the UI thread or not. Thus, any
%methods that calls the checking method must be invoked in the UI thread.

\item \textbf{Safe UI methods: } two helper methods (\CodeIn{View.post}
and \CodeIn{View.postDelay}) that execute code on the UI thread. 
Invoking them on any thread will not cause an invalid thread access error.
%Invoking these two methods are generally considered to be safe, and would not
%cause an invalid thread access error.

\end{itemize}

Instantiating our general technique to  a specific framework
requires moderate human effort. We wrote around 500 lines of Java code in total to achieve
the above four instantiations.

>>>>

We first give a high-level formulation of the problem, then present
the error detection algorithm. Finally, we present how to 
construct a reflection-aware call graph and filter the error reports.

@@

Our algorithm in Figure~\ref{fig:detectalgorithm} %works as follows. It
first constructs a static call graph for the tested program (line 2),
then specifies entry nodes, UI-accessing nodes, and safe UI nodes
for it on line 3, 4, and 5, respectively. Lines 3--5 are GUI framework-specific.
As an example, for a SWT desktop application, the entry nodes include
the single main method, UI-accessing nodes include methods
\CodeIn{Widget.checkWidget} and \CodeIn{Display.checkDevice},
and safe UI methods include two SWT helper methods \CodeIn{Display.asyncExec}  and
\CodeIn{Display.syncExec} for message passing. The detailed instantiation
for each supported framework is explained in Section~\ref{sec:platforms}.

The algorithm first performs graph traversal to find
all reachable \CodeIn{Thread.start()}
nodes from each entry node (line 7).
%For each entry node, the algorithm uses standard Breadth First Search (BFS)
%to find all reachable \CodeIn{Thread.start()} nodes (line 7).
Each \CodeIn{Thread.start()} node in a call graph indicates that a new,
non-UI thread is spawned.  The \CodeIn{Thread.start()}
nodes act as the sources in the main graph traversal.
The algorithm uses BFS to search for reachable UI-accessing
methods (lines 11 -- 25).
The algorithm stops the traversal if it reaches a UI-accessing
method (lines 17 -- 19) or a safe UI method (lines 20, 21).
%Specifically, it uses a queue to keep track of the nodes to be visited (line 7),
%and stores all visited nodes to avoid infinite loop (line 8).
%The algorithm checks every successive node to be visited (line 16):
%it reports an error if that node is a UI-accessing method (lines 18, 19), or skips
%it if it is a safe UI method (lines 20, 21), or simply keeps traversing otherwise (line 23).

The error message created by the method \CodeIn{createErrorReport} on line 18
includes the method call chain from the entry node to the UI-accessing node
as the error report. For brevity, we do not show the data structures that store
the current call chain.
Figure~\ref{fig:report} shows a method call chain from the entry
node \CodeIn{LayerView.<init>} to the UI-accessing node \CodeIn{ViewRoot}.\CodeIn{checkThread}.
%Note that when the algorithm determines that a UI-accessing method may be invoked
%by a non-UI thread, it computes a method call chain from the entry node to
%the UI-accessing node as the error report.
% does that.

\begin{figure}[t]
\textbf{Input}: a Java program $\mathit{P}$\\
\textbf{Output}: a set of potential invalid thread access errors\\
%\textbf{Auxiliary Methods:}\\
%getSuccNodes($\mathit{g}$, $\mathit{n}$): return node $\mathit{n}$'s successive
%nodes in the graph $\mathit{g}$\\
\vspace{-4mm}
\begin{algorithmic}[1]
\STATE $\mathit{errors}$ $\leftarrow$ $\emptyset$ 
\STATE $\mathit{cg}$ $\leftarrow$ constructCallGraph($\mathit{P}$)
\STATE $\mathit{entryNodes}$ $\leftarrow$ getEntryNodes($\mathit{cg}$)
\STATE $\mathit{uiAccessingNodes}$ $\leftarrow$ getUIAccessingNodes($\mathit{cg}$)
\STATE $\mathit{safeUINodes}$ $\leftarrow$ getSafeUINodes($\mathit{cg}$)\\
\FOR{each $\mathit{entryNode}$ in $\mathit{entryNodes}$}
\STATE $\mathit{threadStarts}$ $\leftarrow$ getReachableStarts($\mathit{entryNode}$)\\
\COMMENT{keep the nodes to be visited next in a worklist}
\STATE $\mathit{worklist}$ $\leftarrow$ an empty queue\\
\STATE $\mathit{worklist}$.enqueueAll($\mathit{threadStarts}$)
\STATE $\mathit{visited}$ $\leftarrow$ $\emptyset$
\WHILE{$\mathit{worklist}$.isNotEmpty()}
\STATE $\mathit{node}$ $\leftarrow$ $\mathit{worklist}$.dequeue()
\IF{$\mathit{node}$ $\in$ $\mathit{visited}$}
\STATE continue
\ENDIF
\STATE $\mathit{visited}$ $\leftarrow$ $\mathit{visited}$ $\cup$ $\mathit{node}$
\IF{$\mathit{node}$ $\in$ $\mathit{uiAccessingNodes}$}
\STATE $\mathit{newError}$ $\leftarrow$ createErrorReport($\mathit{node}$)
\STATE $\mathit{errors}$ $\leftarrow$ $\mathit{errors}$ $\cup$ $\mathit{newError}$
\ELSIF{$\mathit{node}$ $\in$ $\mathit{safeUINodes}$}
\STATE continue
\ELSE
\STATE $\mathit{worklist}$.enqueueAll(getSuccNodes($\mathit{cg}$, $\mathit{node}$))
\ENDIF 
\ENDWHILE
\ENDFOR
\RETURN $errors$
%\ENDWHILE
\vspace{-2mm}
\end{algorithmic}
\caption{Algorithm for detecting invalid thread access errors in multithreaded GUI programs. 
Any call graph construction algorithm can be used (line 2). The algorithm
is parameterized by the three methods in lines 3--5 which are specific to each GUI framework
 as described in Section~\ref{sec:platforms}.
} \label{fig:detectalgorithm}
\end{figure}

@@

\subsection{Call Graph Construction}

Given a sound call graph, our algorithm is sound in that it does not
miss true positives. We note, however, that computing a sound
call graph in the presence of reflection and native methods is non-trivial. 
To alleviate this problem, we next proposed a reflection-aware call graph
construction algorithm in Section~\ref{sec:cg} and annotation support
for native methods in Section~\ref{sec:annotation}.

\subsubsection{Reflection}
\label{sec:cg}

@@

When analyzing the code in Figure~\ref{fig:sampleandroid}, existing call graph algorithms
fail to conclude that the variable \CodeIn{button} declared at line 6
points to a \textit{non-null} \CodeIn{Button} object due to its limitation in deal with the
reflection call \CodeIn{findViewById}, and exclude the calling edge
corresponding to the \CodeIn{setText} method call on line 10 in the resulting call graph.

%. As a result, the built 
%call graph will exclude the calling edge corresponding to the
%\CodeIn{setText} method call on line 10.

@@

As demonstrated in our experiments, using this reflection-aware call
graph construction algorithm helps in detecting errors
in Android applications (Section~\ref{sec:reflectionaware}).

@@

\noindent Our static analysis takes the call relationship specified by this
annotation into consideration when traversing the call graph. 
Adding annotations for native methods is optional and requires manual effort.
In our experiments, 1 out of \subnum programs uses native methods. We manually
searched the source files, inspected the code to determine possible target methods
that may be called by a native method, and added \annotationnum annotations for this program.
We found such an annotation was useful: one error
is only reported when using the user-provided annotations.

\subsection{Filtering the Error Reports}
\label{sec:heuristic}

A static analysis can exhaustively check possible error paths; but may report
paths that do not actually exist (false positives) or multiple paths
 that have the same error cause (redundant warnings). We devise
5 error filters below to remove likely false positives and redundant warnings.
The first 2 filters are sound in that they will not filter real bugs, and
other 3 filters are based on heuristics. Orthogonally, filters 2
and 3 are for eliminating false positives, and filters 1, 4, and 5
are for reducing redundant warnings.

%1 - subsumed, 2 - user annotated, 3 - sysem call, 4 heand  5,  tail

@@

%\item

\subsubsection{Sound Filters}

\textbf{1. Filter Lexically Redundant Reports}. One reported method call
chain can lexically subsume another one. For example, suppose that two
reported method call chains: \CodeIn{a()} $\rightarrow$ \CodeIn{b()}
$\rightarrow$ \CodeIn{c()} and 
\CodeIn{d()} $\rightarrow$ \CodeIn{a()} $\rightarrow$ \CodeIn{b()} $\rightarrow$ \CodeIn{c()}
both lead to a potential error, since $\CodeIn{d()}$ and \CodeIn{a()}
are two distinct entry methods. The second call chain should
be removed and would not reduce the error detection capability, since
the first chain reveals the same error and is shorter 
for programmers to interpret.

%\item
\textbf{2. Filter Reports With User-Annotated Methods}. Besides general
library calls, users are also permitted to explicitly annotate project-specific methods
that will never trigger an error.
%For example, the Android GUI framework provides a utility method 
%\CodeIn{runOnUIThread} to check whether the current thread is the UI thread
%before executing the code. If the current thread is not the UI thread,
%this method will be executed on the UI thread via message passing.
%Thus,
A reported method call chain containing an annotated  method
can be safely removed. In our experiments, we produced a list of \filternum
annotated methods for two subjects because they are using a customized
pattern to interact with the GUI framework.

%during analyzing programs on different GUI frameworks; we did this
%only between experiments rather than biasing experiments by tuning
%our tool to specific programs.

\subsubsection{Heuristic Filters}
%\item

\textbf{3. Filter Reports Containing Library Calls}. A
method call chain containing certain library calls
like \CodeIn{Runtime.}\CodeIn{shutDown} are unlikely to
be buggy. For example, the \CodeIn{Runtime.}\CodeIn{shutDown}
method is called when JVM terminates, and uses multithreading
to dispose all GUI objects when the program exits.
We encoded a list of 25 common library calls by proposing
a basic set of library calls that seemed natural and
generally applicable, based on our programming experience.
We later added other calls we found helpful in analyzing
programs and that we believed would be generally useful.

\textbf{4. Filter Report With the Same Head Methods from the Entry Node to \CodeIn{Thread.start()}}. A method can call
multiple methods that access GUI objects, such as:
\vspace{-2mm}
\begin{CodeOut}
\begin{alltt}
     public void m() \{
         accessUIObject1();
         accessUIObject2();
     \}
\end{alltt}
\end{CodeOut}
\vspace{-2mm}
If method \CodeIn{m()} is invoked by a non-UI thread, method call chains that
only differ in the last few method nodes may be reported separately, such as:

@@

As we will show in our experiments (Section~\ref{sec:filters}), these filters
work remarkably well by reducing over 99\% of the reported warnings. In addition,
we also found that only using sound filters was not sufficient. The overwhelming
number of warnings after applied sound filters motivated the use
of heuristic filters.
